Plant-pollintor networks worldwide are composed by the same specific building

### 2021-06-02 Draft/Draft.Rmd
Intro... More or less everything there. Needs some deep reading

Indirect interactions are a widespread phenomenon in ecological communities [@strauss1991]. For instance, plant species can facilitate or compete for pollinator's visitation. Despite their relevance in ecological communities, plant-pollinator research fails to capture indirect interactions with the traditional analytical tools that condense the information in single indices (e.g., netedness or interaction frequency). Nonetheless, the emerging framework of network motifs in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019]. Motifs are cosidered the building blocks that depict subsets of interactions of the network. The work of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions However, we still ignore what are the general patterns of indirect interactions in plant-pollinator networks.

Although past studies have evaluated the ecological implications of motifs [@stouffer2012; @simmons2019], motifs are abstract representations often decoupled from species ecology. Species with different reproductive strategies may occupy different positions and be represented in different motifs. At the micro-scale, @tur2013 have linked the degree of pollinator dependence with specialization. However, meso-scale studies have not evaluated the implications and potential of considering the species reproductive strategy.

Here, we used 60 plant-pollinator networks from 18 different studies and grouped the different plant species into functional groups that represented different reproductive strategies by using a comprehensive dataset with several floral, reproductive and vegetative traits. In addition, we classified pollinator species based on life form and bevavior into different functional groups. Then, we used explored the general patterns of motifs in these plant-pollinator networks

@@

First, plant species were grouped into the optimal number of functional groups that summarized the main plant reproductive strategies. This was done with the help of hierarchical cluster analysis by using the trait dataset compiled in Lanuza et al., (unpublished). This dataset consisted on x floral, x reproductive and x vegetative traits (Table S2). For this, we calculated the distance of the different functional traits with the function gowdis from the package FD version 1.0-12 (Laliberté et al., 2014) with the method ward.D2 used for non-squared distances (Murtagh & Legendre, 2014). All the numerical traits were previously scaled. Finally, we applied a hierarchical cluster analysis with the function hclust from the R stats package version 4.0.5 and calculated the optimal number of clusters with the function kgs from the package maptree version 1.4-7 (White & Gramacy, 2009).

@@

Following Simmons et al. [@simmons2019,@simmons2020], we broke down the plant-pollinator networks into their constituent motifs. Prior to analyses, we selected only robust links, that is, interactions whose frequency was greater than one (64.94 % interactions); and, then, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 1. Adapted figure of Simmons et al., 2019 with all the possible motifs from two to five species in bipartite plant-pollinator networks", fig.width=10,fig.height=8}
library(tidyverse)
library(RColorBrewer)
source("../Scripts/Scripts_Alfonso/plot_motif_positionsV2.R")

@@

>>>>

Indirect interactions are a widespread phenomenon in ecological communities [@strauss1991]. For instance, plant species can facilitate or compete for pollinator's visitation. Despite their relevance in ecological communities, plant-pollinator research fails to capture indirect interactions with the traditional analytical tools that condense the information in single indices (e.g., netedness or interaction frequency). Nonetheless, the emerging framework of network motifs in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019]. Motifs are commonly referred as the building blocks that depict subsets of interactions of the network [@milo2002]. The work of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions. However, we still ignore what are the general patterns of indirect interactions in plant-pollinator networks.

Linking the structural porperties of the meso-scale with the species ecology can help the understanding of ecological processes. For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015]. However, motifs are abstract representations often decoupled from species ecology. Remarkably, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021]. Further, although some studies have evaluated plant reproductive strategies in plant-pollinator networks [tur2013; @lazaro2020], they are often overlooked [@devaux2014]. Hence, exploring how the main species reproductive groups integrate with the emergent motif framework can shed light of key aspects of ecosystem functioning.

Here, we used 60 plant-pollinator networks from 18 different studies and grouped the different plant and pollinator species into functional groups that summarized the main reproductive strategies. Plants were grouped based on a comprehensive dataset that included floral, reproductive and vegetative traits compiled in Lanuza et al., (unpublished) on a larger set of plant-pollinator networks. Pollinators were grouped into the main taxonomical groups that differed in life form and behaviour. Then, we explored the frequency of motifs up to five nodes in these set of plant-pollinator networks. Finally, we explore if the different plants and pollinators functional groups are over- or under-represented by comparing their frequencies with simulated networks.

@@

First, plant species were grouped into the optimal number of functional groups that summarized the main plant reproductive strategies. This was done with the help of hierarchical cluster analysis by using the trait dataset compiled in Lanuza et al., (unpublished). This dataset consisted on x floral, x reproductive and x vegetative traits (Table S2). For this, we calculated the distance of the different functional traits with the function gowdis from the package FD version 1.0-12 [@laliberte2014] with the method ward.D2 used for non-squared distances [@murtagh2014]. All the numerical traits were previously scaled. Finally, we applied a hierarchical cluster analysis with the function hclust from the R stats package version 4.0.5 and calculated the optimal number of clusters with the function kgs from the package maptree version 1.4-7 [@white2009].

@@

Following Simmons et al. [@simmons2019; @simmons2020], we broke down the plant-pollinator networks into their constituent motifs. Prior to analyses, we selected only robust links, that is, interactions whose frequency was greater than one (64.94 % interactions); and, then, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 1. Adapted figure of Simmons et al., 2019 with all the possible motifs from two to five species in bipartite networks", fig.width=10,fig.height=8}
library(tidyverse)
library(RColorBrewer)
source("../Scripts/Scripts_Alfonso/plot_motif_positionsV2.R")

@@

Figure S1
